 

### 2020-09-28 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

![(*For latest version of table, see tables.pdf.*)](table2.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below (easiest in alphabetical order)
```
---
nocite: | 
  @bolstad_foliar_1999; @roberts_stomatal_1990; @slot_photosynthetic_2019 
---

>>>>

![(*For latest version of table, see tables.pdf.*)](table2.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below (easiest in alphabetical order)
```
---
nocite: | 
  @bolstad_foliar_1999; @roberts_stomatal_1990; @slot_photosynthetic_2019; @harleyEffectsLightTemperature1996; @niinemetsHowLightTemperature2015; @sharkeyFutureIsopreneEmission2014b; @ishiiExploringRelationshipsCanopy2004; @curtis_intracanopy_2019; @bolstad_foliar_1999; @kafutiFoliarWoodTraits2020; 
---
